
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 6,
  fig.path = "inst/figure/")
```

# sankey

> Sankey Diagrams

[![Linux Build Status](https://travis-ci.org/MangoTheCat/sankey.svg?branch=master)](https://travis-ci.org/MangoTheCat/sankey)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/MangoTheCat/sankey?svg=true)](https://ci.appveyor.com/project/gaborcsardi/sankey)
[![](http://www.r-pkg.org/badges/version/sankey)](http://www.r-pkg.org/pkg/sankey)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/sankey)](http://www.r-pkg.org/pkg/sankey)
[![Coverage Status](https://img.shields.io/codecov/c/github/MangoTheCat/sankey/master.svg)](https://codecov.io/github/MangoTheCat/sankey?branch=master)

Sankey plots illustrate the flow of information or material.

## Installation

```{r eval = FALSE}
devtools::install_github("mangothecat/sankey")
```

## Usage

```{r}
library(sankey)
```

The API of the package is very simple. You can create a `sankey` object
with `make_sankey`, and plot it with `sankey`. `make_sankey` takes at
least one data frame that defines the edges of the plot. This should be a
data frame, with the starting points of the edges in the first column,
and the end point of the edges in the second column. Both must character
vectors.

Here is a simple example that shows function calls in the
[pkgsnap](https://github.com/mangothecat/pkgsnap) package:

```{r}
edges <- read.table(stringsAsFactors = FALSE, textConnection(
"                get_deps          get_description
                 get_deps               parse_deps
                 get_deps                     %||%
                 get_deps            drop_internal
          get_description        pkg_from_filename
               parse_deps                 str_trim
                cran_file             get_pkg_type
                cran_file          r_minor_version
            download_urls split_pkg_names_versions
            download_urls                cran_file
             pkg_download               dir_exists
             pkg_download            download_urls
             pkg_download        filename_from_url
             pkg_download             try_download
                  restore             pkg_download
                  restore        drop_missing_deps
                  restore            install_order
                  restore                 get_deps
 split_pkg_names_versions               data_frame
"))
pkgsnap_sankey <- make_sankey(edges = edges)
sankey(pkgsnap_sankey)
```

## Customization

Several properties of the plot can be customized by setting extra columns
in the data frame that define the edges, or another data frame, that
defines the nodes.

Current list of graphical parameters for edges:
 *  `colorstyle` Whether the to use a solid color (`col`),
    or `gradient` to plot the edges. The color of a gradient
    edges is between the colors of the nodes.
 *  `curvestyle` Edge style, `sin` for sinusoid curves,
    `line` for straight lines.
 *  `col` Edge color, for edges with solid colors.
 *  `weight` Edge weight. Determines the width of the edges.

Current list of graphical parameters for nodes:
 *  `col` Node color.
 *  `size` Node size.
 *  `x` Horizontal coordinates of the center of the node.
 *  `y` Vertical coordinates of the center of the node.
 *  `shape` Shape of the node. Possible values:
    `rectangle`, `point`, `invisible`.
 *  `lty` Lite type, see `par`.
 *  `srt` How to rotate the label, see `par`.
 *  `textcol` Label color.
 *  `label` Label text. Defaults to node name.
 *  `adjx` Horizontal adjustment of the label. See
    `adj` in the `par` manual.
 *  `adjy` Vertical adjustment of the label. See
    `adj` in the `par` manual.
 *  `boxw` Width of the node boxes.
 *  `cex` Label size multiplication factor.
 *  `top` Vertical coordinate of the top of the node.
 *  `center` Vertical coordinate of the center of the node.
 *  `bottom` Vertical coordinate of the bottom of the node.
 *  `pos` Position of the text label, see `par`.
 *  `textx` Horizontal position of the text label.
 *  `texty` Vertical position of the text label.

Here is the same plot again, with some customization.

```{r}
nodes <- data.frame(
  stringsAsFactors = FALSE,
  id = c("snap", sort(unique(c(edges[,1], edges[,2]))))
)
nodes$col <- ifelse(nodes$id %in% c("snap", "restore"), "orange", "#2ca25f")
edges$colorstyle <- "gradient"

sankey(make_sankey(nodes, edges))
```

We colored the nodes of the exported functions orange, and also added
a color gradient along the edges.

## License

GPL (>= 2) © [Mango Solutions](https://github.com/mangothecat), January Weiner
